Unshuffling Permutations

### 2015-09-27 submission.tex
typos

    (\emph{1} $\Rightarrow$ \emph{2}).
    Since $\pi$ is a square, it admits a square root $\sigma$. Then, by
    definition, there are two sets $I^1 = \{i^1_1 < i^1_2 < \dots < i^1_n\}$
    and $I^2 = \{i^2_1 < i^2_2 < \dots < i^2_n\}$ of disjoint indexes of
    letters of $\pi$ such that $\pi_{|I^1}$ and $\pi_{|I^2}$ are both
    order-isomorphic to $\sigma$. Let $2n = |\pi|$ (and hence
    $|\sigma| = n$). Let $G_\pi$ be the linear clique associated to $\pi$
    with vertices
    $\VS{G_\pi} = \{i^1_j : j \in [n]\} \cup \{i^2_j : j \in [n]\}$. It
    is easily seen that $\mathcal{M} = \{\{i^1_j, i^2_j\} : j \in [n]\}$
    is a subset of $\ES{G_\pi}$. Furthermore, $\mathcal{M}$ is a perfect
    matching since $I^1 \cap I^2 = \emptyset$, and
    $I^1 \cup I^2 = \{1, 2,  \dots 2n\}$. It is also containment-free.
    Indeed, if it is not the case then there would exist two edges
    $e = \{i^1_j, i^2_j\}$ and $e' = \{i^1_k, i^2_k\}$, $j < k$, in
    $\mathcal{M}$ such that $i^1_j < i^1_k < i^2_k < i^2_j$ or
    $i^1_j < i^2_k < i^1_k < i^2_j$. This is a contradiction since
    $i^2_k > i^2_j$ if $k > j$. Finally, for any two distinct edges
    $e = \{\i^1_j, i^2_j\}$ and $e' = \{i^1_k, i^2_k\}$ of $\mathcal{M}$,
    we have $\pi(i^1_j) < \pi(i^2_j)$ if and only if
    $\pi(i^1_k) < \pi(i^2_k)$ since we are comparing in both cases two
    elements (at position $j$ and $k$) in two patterns that are
    order-isomorphic to $\sigma$.

>>>>

    (\emph{1} $\Rightarrow$ \emph{2}).
    Since $\pi$ is a square, it admits a square root $\sigma$.
    Let $2n = |\pi|$ (and hence
    $|\sigma| = n$).
    By definition, there are two sets $I^1 = \{i^1_1 < i^1_2 < \dots < i^1_n\}$
    and $I^2 = \{i^2_1 < i^2_2 < \dots < i^2_n\}$ of disjoint indexes of
    $\pi$ such that $\pi_{|I^1}$ and $\pi_{|I^2}$ are both
    order-isomorphic to $\sigma$.
    Let $G_\pi$ be the linear clique associated to $\pi$ with vertices
    $\VS{G_\pi} = \{i^1_j : j \in [n]\} \cup \{i^2_j : j \in [n]\}$. It
    is easily seen that $\mathcal{M} = \{\{i^1_j, i^2_j\} : j \in [n]\}$
    is a subset of $\ES{G_\pi}$. Furthermore, $\mathcal{M}$ is a perfect
    matching since $I^1 \cap I^2 = \emptyset$, and
    $I^1 \cup I^2 = \{1, 2,  \dots 2n\}$. It is also containment-free.
    Indeed, if it is not the case then there would exist two edges
    $e = \{i^1_j, i^2_j\}$ and $e' = \{i^1_k, i^2_k\}$, $j < k$, in
    $\mathcal{M}$ such that $i^1_j < i^1_k < i^2_k < i^2_j$ or
    $i^1_j < i^2_k < i^1_k < i^2_j$. This is a contradiction since
    $i^2_k > i^2_j$ if $k > j$. Finally, for any two distinct edges
    $e = \{\i^1_j, i^2_j\}$ and $e' = \{i^1_k, i^2_k\}$ of $\mathcal{M}$,
    we have $\pi(i^1_j) < \pi(i^2_j)$ if and only if
    $\pi(i^1_k) < \pi(i^2_k)$ since we are comparing in both cases two
    elements (at position $j$ and $k$) in two patterns that are
    order-isomorphic to $\sigma$.
